Plots

### 2023-09-12 Code/Plots.Rmd
Made orange graph white, moved title in stack graph to inside

```{r}
library(gridExtra)
rank_scatter <- grid.arrange(rank1, rank2, rank3, ncol = 1)
ggsave(filename = "RankScatterPlots.pdf", path = "../Manuscript", plot=rank_scatter, height = 9, width = 7)
```

>>>>

```{r}
library(gridExtra)
rank_scatter <- grid.arrange(rank1, rank2, rank3, ncol = 1)
ggsave(filename = "RankScatterPlots.pdf", path = "../Manuscript", plot=rank_scatter, height = 8, width = 6)
```
